\chapter*{Preface}


This Master's Thesis would not have been possible without the help of those who helped me during production process. For this reason I would like to specifically thank a few people.

This Master's Thesis would not have been possible without the help of those who aided me during the entire process. For this reason I would like to specifically thank a few people. 
\npar
First and foremost I would like to thank my counselors: Dr. Dimitri Staessens and Sander Vrijders. Without their close guidance right from the start of the thesis up until the very last moment, this Thesis would not have been possible. Thanks to their support I was able to learn invaluable knowledge about the subjects concerning this Master's Thesis. 
\\
Beside my counselors I would like to thank my promotor: Dr. Ir. Koen Casier. He provided helpful advice with the writing of the Thesis. Furthermore was he an immense help with the logistics that came coupled with the combination of an exchange program and this Master's Thesis. 
\npar
Finally I would like to my family who supported me during this Master Thesis and my friends who proofread my Master Thesis. Furthermore I would like to extend my gratitude towards the many people who helped me during the process of acquiring information. This includes the many people over at XDA-Developers, the Linux Wireless Kernel mailing list, the i9100 Cyanogenmod team, \ldots.
\npar
Finally I would like to my family who supported me during this Master Thesis and my friends who proofread my Master Thesis. 

\vfill

\begin{flushright}
	Mathieu Devos
	\\
	June 2014 \\
	\rule{90pt}{0.4pt}
\end{flushright}
